### 2012-08-20 whitepaper/pixel_level.tex
pixel signal models

@@

We have shown with large optical imaging surveys that the redundant
information coming from the multiple observations of stars is
sufficient to infer the large-scale sensitivity (effective area or
flat-field or vignetting) of an astronomical imaging device
(\citealt{ubercal}, \citealt{holmes}).  In these self-calibration
experiments, the sensitivity function has had only hundreds or
thousands of parameters.  We have not attempted to obtain millions of
pixel-level parameters from the data and we have not considered
arbitrarily non-smooth two-dimensional sensitivity functions.

@@

\begin{thebibliography}{70}
\bibitem[Padmanabhan \etal(2008)]{ubercal}
Padmanabhan,~N., Schlegel,~D.~J., Finkbeiner,~D.~P., \etal, 2008, \apj, 674, 1217
\bibitem[Holmes \etal(2012)]{holmes}
Holmes,~R., Hogg,~D.~W., \& Rix,~H.-W., 2012, arXiv:1203.6255 
\end{thebibliography}

>>>>

\newcommand{\expectation}[1]{\tilde{#1}}
\newcommand{\sky}{^{(\mathrm{sky})}}

@@

We have shown with large optical imaging surveys that the redundant
information coming from the multiple observations of stars is
sufficient to infer the large-scale sensitivity (effective area or
flat-field or vignetting) of an astronomical imaging device
(\citealt{ubercal}, \citealt{schlafly}, \citealt{holmes}).  In these
self-calibration experiments, the sensitivity function has had only
hundreds or thousands of parameters.  We have not attempted to obtain
millions of pixel-level parameters from the data and we have not
considered arbitrarily non-smooth two-dimensional sensitivity
functions.

@@

\paragraph{varying levels of dumbness:}
There are various thought experiments or considerations that suggest
that a pixel-level self-calibration is possible.  One observation is
that if a pixel is unusually low in sensitivity, it's mean output
signal will be low on average for the whole data set.  This statement
could be made more precise for the sky flat by considering only
observations in which the pixel is not near any detectable source.  It
could be made even more precise if each observation is divided by the
mean pixel value, to account for variations in sky brightness.  These
kinds of operations or considerations could lead to a very good sky
flat for any device, and is not unlike what is usually done.

As we said, however, each pixel might have a different response to
compact sources than it does to the diffuse sky, so slightly less-dumb
methods might be called for.  For example, consider all overlapping
$3\times 3$-pixel patches in a full data set.  Most of these patches
would be far from any detectable source and could be labeled ``sky''.
A fraction would be near or on top of compact, detected sources and
could be labeled ``source''.  This labeling could be
non-comprehensive; there could be intermediate patches labeled
``neither''; this is just an engineering consideration.  Less dumb
still would be to make bigger patches (say $5\times 5$ or larger) or
to make use of the residuals away from a physically motivated model of
the observed images.

\paragraph{pixel signal models}
Sticking with the intermediate level of dumbness for now: In a set of
$3\times 3$ sky patches, the expected signal
$\expectation{D}_{ij}$---the expected number of electrons or data
numbers read out---in pixel $i$ of exposure $j$ might be a combination
of zero-level, dark-current, and sky-photon signals
\begin{equation}
\expectation{D}_{ij} = z_i + d_i\,t_j + f\sky_i\,S\sky_j\,t_j
\end{equation}
where $i$ labels the device pixel ($i$ maps back to a pixel location
in the original imaging device), $j$ labels the exposure, each of
which might have a slightly different sky level, $z_i$ is a zero-level
or bias for pixel $i$, $d_i$ is a dark current rate or signal per time
in the absence of illumination, $t_j$ is the exposure time for
exposure $j$, $f\sky_i$ is the sensitivity of pixel $i$ to diffuse sky
illumination, and $S\sky_j$ is the intensity of the sky in exposure
$j$ (interpolated to pixel $i$ if there are gradients).

In a $3\times 3$ source patch, the expectation is similar...
\begin{equation}
\expectation{D}_{ij} = z_i + d_i\,t_j + f\sky_i\,S\sky_j\,t_j
\end{equation}

\begin{thebibliography}{70}
\bibitem[Holmes \etal(2012)]{holmes}
Holmes,~R., Hogg,~D.~W., \& Rix,~H.-W., 2012, arXiv:1203.6255 
\bibitem[Padmanabhan \etal(2008)]{ubercal}
Padmanabhan,~N., Schlegel,~D.~J., Finkbeiner,~D.~P., \etal, 2008, \apj, 674, 1217
\bibitem[Schlafly \etal(2012)]{schlafly}
Schlafly,~E.~F., Finkbeiner,~D.~P., Juric,~M., \etal, 2012, arXiv:1201.2208 
\end{thebibliography}
